Cradles of the first stars: self-shielding, halo masses, and multiplicity

### 2019-08-27 referee.tex
Adding some comments and minor changes to the response

The 10 pc quoted above is a parameter called StarClusterCombineRadius, and controls how many stars form within a certain spatial range. Within our original simulation, this parameter was set to 10 pc, meaning that all stars younger than 10 kyr and within 10 pc of each other are merged into a single star. To make sure that this value does not affect our results, we have run simulations for a range of this parameter, namely from 0.625 pc to the original 10 pc. The simulations are a 1 comoving Mpc$^3$ box, zoomed-in on a single halo with a mass of $10^{7.7} M_{\odot}$ at the end of the run. The simulations run for a total of 10 Myr. We see the same number of Pop III stars form regardless of the chosen value for the merging parameter. Thus, our results are independent of this value. This detail has been added to section 2.2.1.

@@

@@

I -- In Wise+12, three different environment regions are picked. Please provide more description on the rare peak simulation here and discuss why this one is appropriate in this context.
\end{referee}
RP stands for radiation pressure in Wise+12, not rare peak. The simulation is the same size as ours, and contains similar physics, including the radiation pressure and soft UV background, which is why we reference it here. The differences are the inclusion of H2 self-shielding and updated cosmological parameters.

>>>>

The 10 pc quoted above is a parameter called StarClusterCombineRadius, and controls how many stars form within a certain spatial range. Within our original simulation, this parameter was set to 10 pc, meaning that all stars younger than 10 kyr and within 10 pc of each other are merged into a single star. To make sure that this value does not affect our results, we have run simulations for a range of this parameter, namely from 0.625 pc to the original 10 pc. The simulations are a 1 comoving Mpc$^3$ box, zoomed-in on a single halo with a mass of $10^{7.7} M_{\odot}$ at the end of the run. \jhw{Double check the mass. Looking at the projections of the halo, its virial radius is about 100 pc, which corresponds to a halo mass around $10^6 M_\odot$.} The simulations run for a total of 10 Myr. We see the same number of Pop III stars form regardless of the chosen value for the merging parameter. Thus, our results are independent of this value. This detail has been added to section 2.2.1.

@@

\jhw{The referee is asking how our halo mass calculation with $200\rho_c$ compares with the $200\rho_m$ definition in Machacek+01.  I think a better figure would show the halo masses with these two definitions in each axis.  To make the differences more clear, I would add a subpanel that shows the ratio between the two mass calculations.  I would also calculate the mean ratio of the masses to see how it differs to the analytical expectation if we consider an isothermal sphere, whose mass enclosed $M_{\rm enc} \propto r$ and density $\rho \propto r^{-2}$, i.e. the virial radius will be larger in the $200\rho_m$ definition and thus the virial masses will be larger in Machacek+01.}

@@

I -- In Wise+12, three different environment regions are picked. Please provide more description on the rare peak simulation here and discuss why this one is appropriate in this context.
\end{referee}

\jhw{This is good.}

RP stands for radiation pressure in Wise+12, not rare peak of the Renaissance Simulations (Xu et al. 2016). The simulation is the same size as ours, and contains similar physics, including the radiation pressure and soft UV background, which is why we reference it here. The differences are the inclusion of H2 self-shielding and updated cosmological parameters.
